General exp analysis -- 4/18/2018

### 2018-11-03 resistingrhythm/analysis/paper_figures_v3.Rmd
Update fig plots. Tweak same.

```{r, message=FALSE}
# -----------------------------------------------------------------------
# 16: Burst E, with H
exp_code <- 204
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4) # 4

results204 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results204 <- rbind(results204, df)
  }
}

results204 %>%
  filter(rate_k > 0) -> results204

# -----------------------------------------------------------------------
# 15: Sustained E, with H
exp_code <- 201
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3)# , 4)

results201 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results201 <- rbind(results201, df)
  }
}

results201 %>%
  filter(rate_k > 0) -> results201

# -----------------------------------------------------------------------
# 22: Sustained E, with NO H
exp_code <- 200
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3)#, 4)

results200 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results200 <- rbind(results200, df)
  }
}

results200 %>%
  filter(rate_k > 0) -> results200

# -----------------------------------------------------------------------
# 21: Sustained I, with H
exp_code <- 203
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results203 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results203 <- rbind(results203, df)
  }
}

results203 %>%
  filter(rate_k > 0) -> results203

# -----------------------------------------------------------------------
# 23: Sustained I, with NO H
exp_code <- 202
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3)#, 4)

results202 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results202 <- rbind(results202, df)
  }
}

results202 %>%
  filter(rate_k > 0) -> results202

# -----------------------------------------------------------------------
# 30: Burst I, with H
exp_code <- 207
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results207 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results207 <- rbind(results207, df)
  }
}

results207 %>%
  filter(rate_k > 0) -> results207

@@

# --------------------------------------------------------
# No H, E
results200 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results200 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="d.", y="Kappa", x="Osc. rate (Hz)") +
  # # lims(y=c(0, .15)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.35, size=18, face="bold")) -> p1

@@

# -
# With H, E
results201 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results201 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="e.", y="Kappa", x="Osc. rate (Hz)") +
  # lims(y=c(0, .01)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p2

@@

# -
# Rate, no H, E
results200 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results200 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

@@

# -
# Rate, with H, E
results201 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results201 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

@@

# Var
results204 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results204 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="darkgoldenrod3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="darkgoldenrod3") +
  labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() + 
  # lims(y=c(0, .01)) +
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5

@@

# -
# Rate
results204 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results204 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

# -
# Rate: burst v sustained
tmp3 <- results201
tmp3$osc_mode <- rep("Sustained", nrow(results201))

tmp4 <- results204
tmp4$osc_mode <- rep("Burst", nrow(results204))

@@

# --------------------------------------------------------
# No H, E
results202 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results202 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

@@

# -
# With H, E
results203 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results203 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

@@

# -
# Rate, no H, E
results202 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results202 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

@@

# -
# Rate, with H, E
results203 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results203 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

@@

# Var
results207 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results207 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

@@

# -
# Rate
results207 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results207 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

@@

# -
# Rate: burst v sustained
tmp3 <- results203
tmp3$osc_mode <- rep("Sustained", nrow(results203))

tmp4 <- results207
tmp4$osc_mode <- rep("Burst", nrow(results207))

>>>>

```{r, message=FALSE}
# -----------------------------------------------------------------------
# 16: Burst E, with H
exp_code <- 214
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4) # 4

results214 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results214 <- rbind(results214, df)
  }
}

results214 %>%
  filter(rate_k > 0) -> results214

# -----------------------------------------------------------------------
# 15: Sustained E, with H
exp_code <- 211
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results211 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results211 <- rbind(results211, df)
  }
}

results211 %>%
  filter(rate_k > 0) -> results211

# -----------------------------------------------------------------------
# 22: Sustained E, with NO H
exp_code <- 210
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results210 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results210 <- rbind(results210, df)
  }
}

results210 %>%
  filter(rate_k > 0) -> results210

# -----------------------------------------------------------------------
# 21: Sustained I, with H
exp_code <- 213
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results213 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results213 <- rbind(results213, df)
  }
}

results213 %>%
  filter(rate_k > 0) -> results213

# -----------------------------------------------------------------------
# 23: Sustained I, with NO H
exp_code <- 212
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results212 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results212 <- rbind(results212, df)
  }
}

results212 %>%
  filter(rate_k > 0) -> results212

# -----------------------------------------------------------------------
# 30: Burst I, with H
# HERE
exp_code <- 217
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results217 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results217 <- rbind(results217, df)
  }
}

results217 %>%
  filter(rate_k > 0) -> results217

@@

# --------------------------------------------------------
# No H, E
results210 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results210 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="d.", y="Kappa", x="Osc. rate (Hz)") +
  # # lims(y=c(0, .15)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p1

@@

# -
# With H, E
results211 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results211 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="e.", y="Kappa", x="Osc. rate (Hz)") +
  # lims(y=c(0, .01)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p2

@@

# -
# Rate, no H, E
results210 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results210 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  # lims(y=c(0, 70)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p3

@@

# -
# Rate, with H, E
results211 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results211 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

@@

# Var
results214 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results214 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="darkgoldenrod3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="darkgoldenrod3") +
  labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() + 
  # lims(y=c(0, .01)) +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p5

@@

# -
# Rate
results214 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results214 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="darkgoldenrod3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="darkgoldenrod3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="c.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  # lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p6

# -
# Rate: burst v sustained
tmp3 <- results211
tmp3$osc_mode <- rep("Sustained", nrow(results211))

tmp4 <- results214
tmp4$osc_mode <- rep("Burst", nrow(results214))

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="g.", y="Norm. rate (Hz)", x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  # lims(y=c(-3, 3)) +
  scale_fill_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(
    legend.position = c(0.15, 2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.3, size=18, face="bold")) -> p7

@@

# --------------------------------------------------------
# No H, E
results212 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results212 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

@@

# -
# With H, E
results213 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results213 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

@@

# -
# Rate, no H, E
results212 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results212 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

@@

# -
# Rate, with H, E
results213 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results213 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

@@

# Var
results217 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results217 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

@@

# -
# Rate
results217 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results217 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

@@

# -
# Rate: burst v sustained
tmp3 <- results213
tmp3$osc_mode <- rep("Sustained", nrow(results213))

tmp4 <- results217
tmp4$osc_mode <- rep("Burst", nrow(results217))
